### 2021-04-14 Chapter-5/Chapter-5.tex
Updates from Overleaf

According to Chi Square Distribution Table, we have the probability $p\approx0.95$ to accept the null hypothesis for the two leakages in Figure~\ref{chapter5:fig:multiple} (a). We have the probability $p\approx0.00$ to accept the null hypothesis for the two leakages in Figure~\ref{chapter5:fig:multiple} (b). Therefore, we infer that the two leakages in Figure~\ref{chapter5:fig:multiple} (a) are independent. And the two leakages Figure~\ref{chapter5:fig:multiple} (b) are dependent. For each leakage points, we use the above method to test if any two leakage sites are independent. We combine them into a leakage are calculate the total amount of the leakage.
\section{Design}
In this section, we explain the implementation of \ctool{}.
we first present the overview of \ctool{}. After that, we discuss some design details to implement \ctool{}.

@@

\textbf{Evaluation setup.} We run all the following experiment in a server machine with Ubuntu 18.04 LTS. The server machine equips with 2.90GHz Intel Xeon(R) E5-2690 CPU with 128GB RAM memory. We use the default compilation settings to build the source code of the software into ELF 64-bit executables with GCC 7.5. The server has many cores, but we do not use all cores during the evaluation. We sometimes run several experiments concurrently. The evaluation time presented in the following section is based on a single-core.

\begin{sidewaystable}
\footnotesize
\caption{Evaluation results overview: Name, Side-channel Leaks\,(Leaks), Secret-dependent Control-flows\,(CF), Secret-dependent Data-flows\,(DA),The number of instructions\,(Program Size), Symbolic Execution\,(SE), and Monte Carlo\,(MC).}\label{chapter5:table:over_result}
\centering
\begin{tabular}{lrrrrrrrrrrrr}\toprule

\textbf{Name}   & \multicolumn{2}{c}{\textbf{Input Data}} &  \multicolumn{3}{c}{\textbf{Output Leakage (bits)}} & \multicolumn{3}{c}{\textbf{Maximum Leakage (bits)}}   & \multicolumn{2}{c}{\textbf{Program Size}}    & \multicolumn{2}{c}{\textbf{Performance}}    \\ 
\cmidrule(lr){2-3}\cmidrule(lr){4-6}\cmidrule(lr){7-9}\cmidrule(lr){10-11}\cmidrule(lr){12-13}& \# & bits & Byte & Cache Line& Page & Byte & Cache Line& Page & LoC & Size & Fuzzing & Comparison
\\\midrule
AES       \\
AES       \\
AES \\
RC4 \\
RC4 \\
RC4 \\
RSA \\
RSA \\
Tiny DNN \\
GDK \\
Total             \\
\bottomrule
\end{tabular}

@@

\subsubsection{Electronic Purse}

@@

\subsection{Case Study: Graphic Libraries}

@@

\begin{figure}
  \centering
  \begin{lstlisting}[xleftmargin=.02\textwidth,xrightmargin=.01\textwidth]
int foo(uint8_t secret){
  uint8_t index = 0, t;
  index = (index+secret)%128; // The index contains secrets
  ...
  if(index == 0){             // Secret-dependent flows
    bar(r, x, n)              // The observation
  }
  ...
}
\end{lstlisting}
  \caption{A code fragment}
  \label{fig:limitation}
\end{figure}

>>>>

According to Chi Square Distribution Table, we have the probability $p\approx0.95$ to accept the null hypothesis for the two leakages in Figure~\ref{chapter5:fig:multiple} (a). We have the probability $p\approx0.00$ to accept the null hypothesis for the two leakages in Figure~\ref{chapter5:fig:multiple} (b). Therefore, we infer that the two leakages in Figure~\ref{chapter5:fig:multiple} (a) are independent. And the two leakages Figure~\ref{chapter5:fig:multiple} (b) are dependent. In this paper, for any two leakage, if $p < 0.03$, we think the two leakage sites are independent. For each leakage points, we use the above method to test if any two leakage sites are independent. We combine them into a leakage are calculate the total amount of the leakage.
\section{Design}
In this section, we explain the implementation of \ctool{}.
we first present the overview of \ctool{}. After that, we discuss some design details to implement \ctool{}.

@@

\textbf{Evaluation setup.} We run all the following experiment in a server machine with Ubuntu 18.04 LTS. The server machine equips with 2.90GHz Intel Xeon(R) E5-2690 CPU with 128GB RAM memory. We use the default compilation settings to build the source code of the software into ELF 64-bit executables with GCC 7.5.

\begin{sidewaystable}
\footnotesize
\caption{Evaluation results overview: Name of the benchmark, The Size of the Input Data, The number of leaked functions, The Maximum Leakage, The size of the benchmark, and The Performance.}\label{chapter5:table:over_result}
\centering
\begin{tabular}{lrrrrrrrrrrrrr}\toprule

\textbf{Benchmark}   & \multicolumn{2}{c}{\textbf{Input Data}} &  \multicolumn{3}{c}{\textbf{\# Leakage Functions}} & \multicolumn{3}{c}{\textbf{Maximum Leakage (bits)}}   & \multicolumn{2}{c}{\textbf{Program Size}}    & \multicolumn{3}{c}{\textbf{Performance}}    \\ 
\cmidrule(lr){2-3}\cmidrule(lr){4-6}\cmidrule(lr){7-9}\cmidrule(lr){10-11}\cmidrule(lr){12-14}& \# & bits & Byte & Cache Line& Page & Byte & Cache Line& Page & LoC & Size & Fuzzing & Comparison & Chi-squared
\\\midrule
Safe Password Checker& 65536& 16.0\\
Unsafe Password Checker & 65536 & 16.0\\
One-byte Lookup Table & 65536 & 16.0\\
Four-byte Lookup Table & 65536 & 16.0\\
AES mbedTLS 2.15 & 65536 & 16.0   \\
AES OpenSSL 1.1.0  & 65536 & 16.0    \\
AES OpenSSL 1.1.1& 65536 & 16.0 \\
AES wolfSSL 4.5.0& 65536 & 16.0\\
AES Libgcrypt 1.8.7& 65536 & 16.0\\
RC4 mbedTLS 2.15& 65536 & 16.0\\
RC4 OpenSSL 1.1.0& 65536 & 16.0\\
RC4 OpenSSL 1.1.1& 65536 & 16.0\\
RC4 wolfSSL 4.5.0& 65536 & 16.0\\
RSA mbedTLS 2.15& 4096 & 12.0\\
RSA OpenSSL 1.1.0& 4096 & 12.0\\
RSA OpenSSL 1.1.1& 4096 & 12.0\\
RSA wolfSSL 4.5.0& 4096 & 12.0\\
RSA Libgcrypt 1.8.7& 4096 & 12.0 \\
Tiny DNN & 12000 & 13.6 &\\
GDK 3.24.23 & 65535 & 16.0 &\\
\bottomrule
\end{tabular}

@@

@@

@@

\begin{figure}
  \centering
  \begin{lstlisting}[xleftmargin=.2\textwidth, xrightmargin=.2\textwidth]
int foo(uint8_t secret){
  uint8_t index = 0, t;
  index = (index+secret)%128; // The index contains secrets
  ...
  if(index == 0){             // Secret-dependent flows
    bar(r, x, n)              // The observation
  }
  ...
}
\end{lstlisting}
  \caption{A code fragment}
  \label{fig:limitation}
\end{figure}
